---
title: 'FLAUDIT: Flywheel Project Audit'
output:
  html_document:
    df_print: paged

params:
  project_name: "gear_testing"
  attachments_csv: "/flywheel/v0/output/attachments.csv"
  seqinfo_csv: "/flywheel/v0/output/seqinfo.csv"
  bids_csv: "/flywheel/v0/output/bids.csv"
  jobs_csv: "/flywheel/v0/output/jobs.csv"
  template: ""
---

```{r, include = FALSE, echo = FALSE, cache = FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width=16, fig.height=12)
```

```{r, include = FALSE, echo = FALSE}
if (!require("pacman")) install.packages("pacman")
if (!require("remotes")) install.packages("remotes")
i <- 1
packs <- c('DT', 'dplyr', 'stringr', 'ggplot2', 'tidyr', 'purrr', 'knitr', 'scales', 'ggrepel', 'wordcloud', 'naniar', 'gdata', 'lubridate', 'collapsibleTree', 'jsonlite', 'data.table', 'readr')

pacman::p_load(DT, dplyr, stringr, ggplot2, tidyr, purrr, knitr, scales, ggrepel, wordcloud, naniar, gdata, lubridate, collapsibleTree, jsonlite, data.table, readr)

install.packages('visdat', 'rlang', 'glue')
remotes::install_github("njtierney/naniar", dependencies = TRUE)
# for(x in packs){
#   print(i)
#   print(x)
#   if(!require(x)){
#     install.packages(x)
#   }
#   pacman::p_load(x)
#   i <- i+1
# }

ggplot_base <- 18
```

```{r, include = FALSE, echo = FALSE}
#library(here)
attachments <- #here('data', 'grmpy', 'attachments.csv') %>% 
  params$attachments_csv %>%
  read_csv() %>%
  filter(!str_detect(Type, "bvec|bval")) %>%
  filter(!(str_detect(Name, "json") & str_detect(Origin_Level, "Acquisition")))

seqinfo <- #here('data', 'grmpy', 'seqinfo.csv') %>% 
  params$seqinfo_csv %>%
  read_csv()# %>%
  #filter(!is.na(series_description))

jobs <- #here('data', 'grmpy', 'jobs.csv') %>% 
  params$jobs_csv %>%
  read_csv()

bids <- #here('data', 'grmpy', 'bids.csv') %>% 
  params$bids_csv %>%
  read_csv()

if(nrow(seqinfo) < 1){
  stop("Seqinfo table is empty!")
}

if(params$template == '') {
  
  warning('Template subject not given, using first subject')
  golden_id <- seqinfo$patient_id[0]
  
} else if(!(params$template %in% seqinfo$patient_id)) {
  
  warning('Template subject not found in project, using first subject')
  golden_id <- seqinfo$patient_id[0]
  
} else {
  
  golden_id <- params$template
  
}
```

## Project: `r params$project_name`

## Number of Subjects: `r length(unique(seqinfo$patient_id))`

## Number of Sessions: `r nrow(distinct(seqinfo, patient_id, session_id))`

## Template Subject: `r golden_id`

---

# Overview {.tabset .tabset-pills}

## Sequences

Here's a list of all the sequences in `r params$project_name`:

```{r, warning=FALSE, echo=FALSE}
sequences <- seqinfo %>%
  group_by(series_description) %>%
  summarise(Freq = n()) %>%
  arrange(-Freq) %>%
  drop_na()

wordcloud(words = sequences$series_description, freq = sequences$Freq)
```

```{r, echo=FALSE}
datatable(sequences)
```

We visualise the above frequencies below:


```{r, echo = FALSE}
ggplot(sequences, aes(x = series_description, y = Freq))+
  geom_bar(stat = 'identity') +
  coord_flip() +
  theme_minimal(base_size = ggplot_base) +
  labs(title = "Raw Frequencies of Sequences in the Project", x = "Sequence Name")
```

```{r, include = FALSE, echo=FALSE}
#And hence, the missingness of sequences across all the subjects in `r params$project_name`:

seq_ns <- unique(seqinfo$series_description) %>%
  na.omit() %>% as.vector()
ids <- unique(seqinfo$patient_id)
output_df <- data.frame(matrix(data = 0, ncol = length(seq_ns), nrow = length(ids)))

names(output_df) <- seq_ns

for(i in 1:length(ids)){

  df <- seqinfo %>%
    filter(patient_id == ids[i])


  for(row in 1:nrow(df)){


    target <- df$series_description[row]

    if(!is.na(target)){
      output_df[i, target] <- output_df[i, target] + 1
    }

  }

}

output_df %>%
  mutate_all(.funs = function(x) ifelse(x == 0, NA, x)) %>%
  naniar::gg_miss_var(show_pct = TRUE) +
  labs(x = "Sequence") +
  theme_minimal(base_size = ggplot_base)
```

## BIDS Curation
The tree diagram below shows how each sequence has been curated into BIDS format. The leaf at the end of each branch counts how many subjects have files that fall under each BIDS template.

```{r, echo = FALSE, message=FALSE}
seqinfo %>%
  # group_by(patient_id, session_id, series_description) %>%
  # slice(1) %>%
  # ungroup() %>%
  select(patient_id, session_id, series_id, series_description) %>%
  distinct() %>%
  filter(complete.cases(.)) %>%
  left_join(distinct(bids), by = c("session_id", "series_id")) %>%
  mutate(
    bids_name = str_replace_all(Filename, "sub-[^_]+(?=_)", "\\{subject\\}"),
    bids_name = str_replace_all(bids_name, "ses-[^_]+(?=_)", "\\{session\\}")
  ) %>%
  select(series_description, Modality, bids_name, patient_id) %>%
  group_by(series_description, bids_name) %>%
  summarise(`Count` = n()) %>%
  # mutate(
  #   `Number of Subjects` = ifelse(is.na(Folder), 0, `Number of Subjects`)
  #
  # ) %>%
  collapsibleTreeSummary(.,
    c("series_description", "bids_name"),
    attribute = "Count", root = params$project_name, width = 1000, height = 800, zoomable = TRUE
  )
```

## Gears Runs & Jobs

There have been `r length(unique(jobs$job_id))` gears run in total, for a total runtime of `r as.character(lubridate::as.duration(sum(jobs$run_runtime_ms)/1000))`. The most commonly run gear is ``r jobs %>% group_by(gear_name) %>% summarise(n = n()) %>% arrange(-n) %>% pull(gear_name) %>% .[1]`` with a total of `r jobs %>% group_by(gear_name) %>% summarise(n = n()) %>% arrange(-n) %>% pull(n) %>% .[1]` runs. The gear with the most version increments is ``r jobs %>% group_by(gear_name) %>% summarise(n = n_distinct(gear_version)) %>% arrange(-n) %>% pull(gear_name) %>% .[1]``.

Here are the raw counts of complete gear runs, using only the most recent version and run of each gear:

```{r, echo = FALSE}
jobs %>%
  filter(run_status == "complete") %>%
  group_by(subject, session, gear_name) %>%
  arrange(subject, session, gear_name, desc(run_datetime)) %>%
  slice(1) %>%
  ungroup() %>%
  group_by(gear_name) %>%
  summarise(n = n()) %>%
  ggplot(aes(x=gear_name, y=n)) +
    geom_col() +
    theme_minimal(base_size = ggplot_base) +
    coord_flip() +
    labs(title = "Raw Count of Complete Gear Runs", x = "Gear Name") +
    NULL
```


Here are the gear completion statistics:

```{r, echo=FALSE}
jobs_plot <- jobs %>%
  # mutate(run_status = factor(run_status)) %>%
  group_by(job_id) %>%
  arrange(run_status) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  group_by(gear_name, run_status) %>%
  summarise(n = n()) %>%
  mutate(freq = n / sum(n),
         perc = percent(freq, accuracy = 1),
         cumsum = cumsum(n)) %>%
  ungroup() %>%
  # mutate(perc = ifelse(freq < 0.2, "", perc)) %>%
  ggplot(aes(x=gear_name, y=n, group = run_status)) +
    geom_bar(aes(fill=run_status), stat = 'identity', position = "dodge") +
    theme_minimal(base_size = 18) +
    scale_fill_viridis_d() +
    geom_label_repel(aes(label = perc, y=n), force = 5, position = position_dodge(0.5)) +
    coord_flip() +
    labs(title = "Gear Runs & Completion Rate", x = "Gear Name") +
    NULL

jobs_plot
```

## Gear Runtime

Below are the runtimes of gear runs:

```{r, echo=FALSE}
jobs %>%
  mutate(run_runtime_ms = run_runtime_ms/1000/60) %>%
  #group_by(gear_name) %>%
  ggplot(aes(x=run_runtime_ms)) +
    geom_histogram(aes(fill = run_status), alpha = 0.5, bins = 25) +
    theme_minimal(base_size = 18) +
    scale_fill_viridis_d() +
    labs(title = "Gear Runtimes", x = "Runtime in Minutes") +
    facet_wrap(~gear_name, scales = "free")
```

## Attachments

There are `r nrow(attachments)` attachments for a total of `r humanReadable(sum(attachments$Size_kb), width=4, standard = "SI")` of data.
```{r, echo=FALSE}
attachments %>%
  ggplot(aes(x=Type)) +
  geom_bar(aes(fill = Origin_Level), alpha = 0.5) +
  theme_minimal(base_size = 18) +
  scale_fill_viridis_d() +
  labs(title = "Attachments Count")# +
  #facet_wrap(~gear_name, scales = "free")
```

# {-}

# Project Completion {.tabset .tabset-pills}

Using subject ``r golden_id`` as the project template, the following sections describe the project's completeness in comparison to the template subject.

## Sequences

The following table displays all the available *scanning sequences* collected from subject ``r golden_id`` as columns. Rows represent each other subject in the project and denote whether they have the correct number of sequences as the template subject. Filters in the column header can be used for quick inspection.

```{r}
wide_seqinfos <- seqinfo %>%
  select(series_description, patient_id) %>%
  group_by(patient_id, series_description) %>%
  summarise(n=n()) %>%
  drop_na(series_description, n) %>%
  pivot_wider(names_from = series_description, values_from=n)

golden_seqinfos <- wide_seqinfos %>%
  filter(patient_id == golden_id) %>%
  select_if(~all(!is.na(.))) %>%
  ungroup()

wide_seqinfos <- wide_seqinfos %>%
  select(tidyselect::any_of(names(golden_seqinfos))) %>%
  ungroup()

compare_rows <- function(test, golden=golden_seqinfos){
  
  comps <- test == select(golden, -patient_id)
  comps_df <- comps %>%
    as_tibble() %>%
    mutate(Complete = all(comps)) %>%
    mutate_all(function(x) ifelse(x, paste0(emo::ji('check'), " complete"), paste0(emo::ji('x'), ' incomplete'))) %>%
    select(Complete, everything())

  return(comps_df)
  
}

comparisons <- wide_seqinfos %>%
  filter(patient_id != golden_id) %>%
  group_by(patient_id) %>%
  nest() %>%
  mutate(result = map(data, compare_rows)) %>%
  unnest(result) %>%
  select(-data) #%>%
  #rename('Complete compared to {golden_id}' := Complete)

comparisons %>%
  ungroup() %>%
  left_join(select(jobs, subject, session), by = c("patient_id" = "subject")) %>%
  select(subject=patient_id, session, everything()) %>%
  mutate_if(is.character, as.factor) %>%
  ungroup() %>%
  distinct() %>%
  datatable(., filter = 'top', extensions = 'FixedColumns',
    options = list(
    dom = 't',
    scrollX = TRUE,
    scrollCollapse = TRUE
    )
  )
```

## BIDS Curation

The following table displays all the available *BIDS data* collected from subject ``r golden_id`` as columns. Rows represent each other subject in the project and denote whether they have the correct number of BIDS files as the template subject. Filters in the column header can be used for quick inspection.

```{r}
full_bids <- seqinfo %>%
  # group_by(patient_id, session_id, series_description) %>%
  # slice(1) %>%
  # ungroup() %>%
  select(patient_id, session_id, series_id, series_description) %>%
  distinct() %>%
  filter(complete.cases(.)) %>%
  left_join(distinct(bids), by = c("session_id", "series_id")) %>%
  mutate(
    bids_name = str_replace_all(Filename, "sub-[^_]+(?=_)", "\\{subject\\}"),
    bids_name = str_replace_all(bids_name, "ses-[^_]+(?=_)", "\\{session\\}")
  ) %>%
  rename(subject=patient_id, session=session_id)

golden_bids <- full_bids %>%
  filter(subject == golden_id, !is.na(bids_name)) %>%
  group_by(subject, session, bids_name) %>%
  summarise(n=n()) %>%
  pivot_wider(names_from = bids_name, values_from=n) %>%
  ungroup()

wide_bids <- full_bids %>%
  filter(!is.na(bids_name)) %>%
  group_by(subject, session, bids_name) %>%
  summarise(n=n()) %>%
  pivot_wider(names_from = bids_name, values_from=n) %>%
  select(tidyselect::any_of(names(golden_bids))) %>%
  ungroup()

compare_rows <- function(test, golden=golden_bids){

  comps <- test == select(golden, -subject, -session)
  comps[is.na(comps)] = FALSE
  comps_df <- comps %>%
    as_tibble() %>%
    mutate(Complete = all(comps)) %>%
    mutate_all(function(x) ifelse(x, paste0(emo::ji('check'), " complete"), paste0(emo::ji('x'), ' incomplete'))) %>%
    select(Complete, everything())

  return(comps_df)

}

comparisons <- wide_bids %>%
  group_by(subject, session) %>%
  nest() %>%
  mutate(result = map(data, compare_rows)) %>%
  unnest(result) %>%
  select(-data) %>%
  select(subject, session, Complete, all_of(names(golden_bids)))

comparisons %>%
  ungroup() %>%
  mutate_if(is.character, as.factor) %>%
  ungroup() %>%
  distinct() %>%
  datatable(., filter = 'top', extensions = 'FixedColumns',
    options = list(
    dom = 't',
    scrollX = TRUE,
    scrollCollapse = TRUE
    )
  )
```


## Gear Runs & Jobs

```{r}
wide_jobs <- jobs %>%
  filter(run_status == 'complete') %>%
  select(gear_name, subject, session, run_datetime, run_status) %>%
  group_by(subject, session, gear_name) %>%
  arrange(run_datetime) %>%
  slice(1) %>%
  ungroup()

jobs_order <- wide_jobs %>% 
  filter(subject==golden_id) %>%
  arrange(run_datetime) %>%
  pull(gear_name)

wide_jobs <- wide_jobs %>%
  group_by(subject, session, gear_name) %>%
  summarise(n=n()) %>%
  pivot_wider(names_from = gear_name, values_from=n)

golden_jobs <- wide_jobs %>%
  filter(subject == golden_id) %>%
  select_if(~all(!is.na(.))) %>%
  ungroup()

wide_jobs <- wide_jobs %>%
  select(tidyselect::any_of(names(golden_jobs))) %>%
  ungroup()

compare_rows <- function(test, golden=golden_jobs){

  comps <- test == select(golden, -subject, -session)
  comps[is.na(comps)] = FALSE
  comps_df <- comps %>%
    as_tibble() %>%
    mutate(Complete = all(comps)) %>%
    mutate_all(function(x) ifelse(x, paste0(emo::ji('check'), " complete"), paste0(emo::ji('x'), ' incomplete'))) %>%
    select(Complete, everything())

  return(comps_df)

}

comparisons <- wide_jobs %>%
  group_by(subject, session) %>%
  nest() %>%
  mutate(result = map(data, compare_rows)) %>%
  unnest(result) %>%
  select(-data) %>%
  select(subject, session, Complete, all_of(jobs_order)) #%>%
  #rename('Complete compared to {golden_id}' := Complete)

jobs_order <- paste0('`',jobs_order, '`') %>%
  paste0(., collapse=emo::ji('arrow_right'))
```

The following table displays all the available *gear runs* collected from subject ``r golden_id`` as columns. Rows represent each other subject in the project and denote whether they have had the same gear run successfully. Filters in the column header can be used for quick inspection.

Note that runs order from left to right (`r paste0(jobs_order, collapse=emo::ji('arrow_right'))`).


```{r}
comparisons %>%
  ungroup() %>%
  mutate_if(is.character, as.factor) %>%
  ungroup() %>%
  distinct() %>%
  datatable(., filter = 'top', extensions = 'FixedColumns',
    options = list(
    dom = 't',
    scrollX = TRUE,
    scrollCollapse = TRUE
    )
  )
```

# {-}

